My title

### 2022-02-05 outputs/paper/paper.Rmd
commit for the day

```{r}
covid_cases <- clean_names(covid_cases)
#covid_cases <- subset(covid_cases, select = -c(1,2,7,8))
```

@@

COVID-19, like many other viruses thrives in colder drier climates and Figure \@ref(fig:figone) . To do this, two new variables named "month_of_ diagnosis" and "year_of_diagnosis" were mutated using the tools from the dplyr package. The following two graphs show the number of covid cases for both 2020 and 2021 as those are the only two complete years that we have have to live with the virus.

```{r figone, echo=FALSE}

@@

monthly_figs <- (fig2020 + fig2021)
monthly_figs + plot_annotation(caption = "Figure 1: COVID-19 Cases for every month in 2020 and 2021")
```
```{r tableone, echo=FALSE}

@@

@@

September <- c(3012,2806)
November <- c(5029, 1932)
December <- c(9047, 3975)

holiday_case <- data.frame(September, November, December)
rownames(holiday_case) <- c("2020","2021")

holiday_case<- knitr::kable(holiday_case, caption = "Table 1: Number of covid cases from contact during holiday months")
holiday_case
```

In 2020, we can see how the number of covid cases were highest during the fall and winter months and how that trend carries onto early 2021 which should be what is expected. The number of cases tend to increase near the winter 2020 and that trend continued in until April 2021 where the cases began to continuously decrease. One thing to notice is that in both years, there are a a higher amount  of COVID cases comparatively speaking to other months. One of the possible reasons explaining this rise in cases during this time is the fact that this is around the holidays when families tend to get together. Table \@ref(tab:tableone) shows the count for COVID-19 cases that were transmitted through contact which includes close contact, household contact and community contact. For both years, we notice that the month of December had the highest number of COVID-19 cases, likely because of Christmas. Another thing to consider is that in December of 2020, there was a new and more contagious variant of the COVID-19 virus called the delta variant. Similarly, at the end of November 2021, we got the omicron variant, one that was even more contagions than the delta variant which also explains the high case counts in December of 2020 and 2021.

@@

ggplot(data = covid_cases, mapping = aes_(x = covid_cases$month_of_diagnosis, fill = covid_cases$age_group)) + 
                         geom_bar(postion = 'stack')

@@

```
These bar charts..

@@

#covid_cases2021 %>% ggplot(mapping = aes(x= age_group)) + geom_bar()

@@

#covid_cases %>% count(month_of_diagnosis)
#covid_cases %>% count(outcome)
#propo <- covid_cases %>% count(source_of_infection)
#type <- unique(covid_cases[c("source_of_infection")])

#prop.table(propo)

#cases_per_year <- covid_cases %>% select(year_of_diagnosis, outcome) 
#API

@@

# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

@@

## Second discussion point

## Third discussion point

@@

# Additional details

>>>>

```{r, echo=FALSE}
covid_cases <- clean_names(covid_cases)
#covid_cases <- subset(covid_cases, select = -c(1,2,7,8))
```

@@

COVID-19, like many other viruses thrives in colder drier climates and (Figure \@ref(fig:month)) the number of cases for every month in 2020 and 2021.  Using the tools from the dplyr package, two new variables named "month_of_ diagnosis" and "year_of_diagnosis" were mutated from the original variable "episode_date" which pertained to the date that the case was confirmed. The following two charts show the number of covid cases for both 2020 and 2021 as those are the only two complete years that we have have to live with the virus.

```{r month, echo=FALSE}

@@

monthly_figs <- (fig2020 / fig2021)
monthly_figs
monthly_figs + plot_annotation(caption = "Figure 1: COVID-19 Cases for every month in 2020 and 2021", theme = theme(plot.caption.position = "plot", plot.caption = element_text(hjust = 0.1)))

```
From Figure \@ref(fig:month), the colder months in the year tend to have the most number of cases where as the summer months have a significantly lower number of cases. In 2020, we can see how the number of covid cases were highest during the fall and winter months and how that trend carries onto early 2021 which should be what is expected. The number of cases increased near the winter 2020 and that trend continued in until April 2021 where the cases began to continuously decrease. Unlike 2021, where we saw an increasing trend in the colder months, for 2021 it seems that the number of cases had stabilized, possibly due to the increased amount of the population that the vaccine had been administered to by then. As part of Ontario's "Phase 2," vaccines had begun to be distributed based off "hot spots" by April of 2021 and eligible to everyone as a part of their "Phase 3" which began in July of 2021.

One of the possible reasons explaining this rise in cases during this time is the fact that this is around the holidays when families tend to get together.

```{r tableone, echo=FALSE}

O <- count(covid_cases2020 %>% 
  filter(month_of_diagnosis == "Oct", source_of_infection == "Close Contact" | source_of_infection == "Community" | source_of_infection == "Household Contact"))

@@

O1 <- count(covid_cases2021 %>% 
  filter(month_of_diagnosis == "Oct", source_of_infection == "Close Contact" | source_of_infection == "Community" | source_of_infection == "Household Contact"))

@@

September <- c(3012,2806)
October <- c(2413,1429)
November <- c(5029, 1932)
December <- c(9047, 3975)

holiday_case <- data.frame(September, October, November, December)
rownames(holiday_case) <- c("2020","2021")

holiday_case<- knitr::kable(holiday_case, caption = "Number of covid cases from contact during holiday months")
holiday_case
```

Table \@ref(tab:tableone) shows the count for COVID-19 cases that were transmitted through contact which includes close contact, household contact and community contact. For both years, we notice that the month of December had the highest number of COVID-19 cases, likely because of Christmas. Another thing to consider is that in December of 2020, there was a new and more contagious variant of the COVID-19 virus called the delta variant. Similarly, at the end of November 2021, we got the omicron variant, one that was even more contagions than the delta variant which also explains the high case counts in December of 2020 and 2021. The vaccines that people had taken until December of 2021 did not necessarily protect them from the omicron variant which is likely to be another reason that December of 2021 had the largest amount of cases for any month.

Another variable this data set gave us was the age group that every case fell under. These age groups ranged from "19 and younger" to "90 and older." The following figure shows the number of cases for every age group.

```{r, echo=FALSE}
age_cases <- covid_cases %>% ggplot(mapping = aes(x= age_group)) + geom_bar() + labs(x = "Age Group", y = "Number of COVID-19 cases") + coord_flip()

age_cases + plot_annotation(caption = "Cases of COVID-19 by age group", theme = theme(plot.caption.position = "plot", plot.caption = element_text(hjust = 0.1)))

```
Figure 3 (change later) shows us that the younger population catches the virus much more compared to the older population, likely because the younger population has more of a reason to be outside the house, whether that be for work or for school. This could also explain the reasoning behind the decisions of closing schools, restaurants, bars and other recreational facilities since these are all places where one is more likely to find a younger audience. Figure 4 gives a more holistic view of the number of covid cases as it incorporates the age group and number of covid cases per month into one graph. For both years, it is evident that those between the ages of 20 and 40 have the highest proportions of cases regardless of which month is looked at.

@@

```{r}
ggplot(data = covid_cases2020, mapping = aes_(x = covid_cases2020$month_of_diagnosis, fill = covid_cases2020$age_group)) + 
                         geom_bar(postion = 'stack')

ggplot(data = covid_cases2021, mapping = aes_(x = covid_cases2021$month_of_diagnosis, fill = covid_cases2021$age_group)) + 
                         geom_bar(postion = 'stack')

@@

```
This dataset is made up of data collected from individuals which means that there is likely to be some sort of ethical considerations. One of the largest concerns with this dataset is that it only accounts for the "confirmed" and "probable cases." This leaves out many categories of cases that likely contain a lot of individuals:

*The individual is unknowingly living with COVID
  + Since the virus does affect every individual differently, there are many cases where the individual isn't even aware of the fact that they have the virus and continue to live with it until it naturally goes away.

* The individual knows they have the virus but refuses to report it

* The individual feels sick but mistake it for the common cold/other virus.

#gender reason as well?

@@

covid_cases %>% count(client_gender)
covid_cases2021 %>% ggplot(mapping = aes(x= age_group)) + geom_bar()

@@

#covid_cases %>% count(month_of_diagnosis)
#covid_cases %>% count(outcome)
#propo <- covid_cases %>% count(source_of_infection)

covid_cases %>% count(age_group)
#cases_per_year <- covid_cases %>% select(year_of_diagnosis, outcome) 
#API

@@

@@

@@
